SDR enhancement by clouds

### 2024-03-05 article/article.Rmd
Commit 2024-03-05 11:13

criteria for cloud enhancement identification are set acording the Equation \ref{eq:CE4}

@@

A secondary criteria was used for extreme cloud enhancement cases (ECE) identification, relative to the TSI at horizontal plane Equation \ref{eq:ECE}

@@

@@

Describe set of referce days we used to evalutate

>>>>

criteria for cloud enhancement identification are set according the Equation \ref{eq:CE4}

@@

A secondary criteria was used for extreme cloud enhancement cases (ECE) identification, relative to the TSI at horizontal plane (Equation \ref{eq:ECE})

@@

Sky Camera for some cases

@@

Describe set of reference days we used to evaluate
